---
title: "Home Activity"
author: "15F-8069"
output:
  pdf_document: default
  html_document:
    df_print: paged
    always_allow_html: yes
---

#Load Dataset
  ```{r}
data("airquality")
```

#Data Exploration
```{r}
str(airquality)
head(airquality, n=3)
tail(airquality, n=3)
summary(airquality)
```

#Getting Started with Basic Plots
```{r}
plot(airquality$Ozone)
plot(airquality$Ozone, airquality$Wind)
plot(airquality)
```

#Using arguments with the plot() function
```{r}
# points and lines 
plot(airquality$Ozone, type= "b")
# high density vertical lines.
plot(airquality$Ozone, type= "h")
```

#Labels and Titles
```{r}
plot(airquality$Ozone, xlab = 'ozone Concentration', ylab = 'No of Instances', main = 'Ozone levels in NY city', col = 'green')
```

# 2.Barplot
```{r}
# Horizontal bar plot
barplot(airquality$Ozone, main = 'Ozone Concenteration in air',xlab = 'ozone levels', col= 'green',horiz = TRUE)
# Vertical bar plot
barplot(airquality$Ozone, main = 'Ozone Concenteration in air',xlab = 'ozone levels', col='red',horiz = FALSE)
```

# 3.Histogram
```{r}
hist(airquality$Solar.R)
#coloured histogram
hist(airquality$Solar.R, main = 'Solar Radiation values in air',xlab = 'Solar rad.', col='red')
```

# 4.Boxplot
```{r}

#Single box plot
boxplot(airquality$Solar.R)

# Multiple box plots
boxplot(airquality[,0:4], main='Multiple Box plots')
```

#5. Grid of Charts
```{r}
par(mfrow=c(3,3), mar=c(2,5,2,1), las=1, bty="n")
plot(airquality$Ozone)
plot(airquality$Ozone, airquality$Wind)
plot(airquality$Ozone, type= "c")
plot(airquality$Ozone, type= "s")
plot(airquality$Ozone, type= "h")
barplot(airquality$Ozone, main = 'Ozone Concenteration in air',xlab = 'ozone levels', col='green',horiz = TRUE)
hist(airquality$Solar.R)
boxplot(airquality$Solar.R)
boxplot(airquality[,0:4], main='Multiple Box plots')
```

#Visualisation libraries in R
```{r}
library(lattice)

#Loading the dataset
attach(mtcars)

# Exploring the dataset
head(mtcars)
gear_factor<-factor(gear,levels=c(3,4,5),
                    labels=c("3gears","4gears","5gears"))
cyl_factor <-factor(cyl,levels=c(4,6,8),
                    labels=c("4cyl","6cyl","8cyl"))
```

# We can use the lattice package to create some basic plots in R.

# Kernel density plots
```{r}
densityplot(~mpg, main="Density Plot",  xlab="Miles per Gallon")
```

#scatterplot matrix
```{r}
splom(mtcars[c(1,3,4,5,6)], main="MTCARS Data")
```

#Scatterplots depicting a combination of two factors
```{r}
xyplot(mpg~wt|cyl_factor*gear_factor,  
       main="Scatterplots : Cylinders and Gears",  
       ylab="Miles/Gallon", xlab="Weight of Car")
```

#ggplot2
```{r}
library(ggplot2)

#Loading the dataset
attach(mtcars)

# create factors with value labels 
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),  
                      labels=c("3gears", "4gears", "5gears"))  
mtcars$am <- factor(mtcars$am,levels=c(0,1),  
                    labels=c("Automatic","Manual"))  
mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),  
                     labels=c("4cyl","6cyl","8cyl"))
```

#create a few plots to understand the capability of ggplot2

#Scatter Plots
```{r}
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg)) + geom_point()
```

#Styling scatter plots by factor
```{r}
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg, color = as.factor(cyl))) + geom_point()
```

#Styling scatter plots by size
```{r}
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg, size = qsec)) + geom_point()
```

#Different symbols for different sizes
```{r}
p  <-  ggplot(mtcars,aes(mpg, wt, shape  =  factor(cyl)))
p + geom_point(aes(colour  =  factor(cyl)), size  =  4) + geom_point(colour  =  "grey90", size  =  1.5)
```

# 3. Plotly
```{r}
library(plotly)
```

#Basic Scatter Plot
```{r}
p <- plot_ly(data = mtcars, x = ~hp, y = ~wt)
p
```

#Styled Scatter Plot
```{r}
p <- plot_ly(data = mtcars, x = ~hp, y = ~wt, marker = list(size = 10, color = 'rgba(255, 182, 193, .9)', line = list(color = 'rgba(152, 0, 0, .8)', width = 2)))
p
```

#Markers and Lines
```{r}
data1 <- rnorm(100, mean = 10)   
data2 <- rnorm(100, mean = 0)   
data3 <- rnorm(100, mean = -10)   
x <- c(1:100)
data <- data.frame(x, data1, data2, data3)
p <- plot_ly(data, x = ~x)%>%   
  
  add_trace(y = ~data1, name = 'data1',mode = 'lines')%>%             
  add_trace(y = ~data2, name = 'data2', mode = 'lines+markers')%>% 
  add_trace(y = ~data3, name = 'data3', mode = 'markers')
p
```

#Adding Color and Size Mapping
```{r}
p <- plot_ly(data = mtcars, x =~hp, y = ~wt,color = ~hp, size = ~hp )
p
```

#Visualising Geographical data in R

# Geographical maps
```{r}
data <- read.csv('ABC_locations.csv', sep=",")
head(data)
```

#plot() function
```{r}
plot(data$Longitude,data$Latitude)
```

#map() function
```{r}
library(maps)
```

#Using the map() function to plot a base map of the US
```{r}
map(database="state")
```

